---
title: "POSTCODE: Download and Unzip ABS Census Data"
author: "Jeremy Forbes"
date: "06/03/2018"
output: html_document
---

## Update

Using postal areas as the Census shapes. 


```{r}
library(RCurl)
library(tidyverse)
```


## Continue

This markdown, when run, downloads the requires Commonwealth Electoral Division community profiles for 2001 and 2006. It then unzips the downloaded files and places them in the folders to be accessed by the Census-to-Dataframe file.

Profiles are split into separate folders for ABS2001 and ABS2006, of which have folders for the Zipped and Unzipped files.

#Download Census data for each POA, 2001

Loop over each post code for 2001
```{r all_2001, eval = FALSE}
url_p1 = "http://www.censusdata.abs.gov.au/CensusOutput/copsub2006.NSF/All%20docs%20by%20catNo/2001~Community%20Profile~POA"
url_p2 = "/$File/BCP_POA"
url_p3 = ".zip?OpenElement"

#urltrue = "http://www.censusdata.abs.gov.au/CensusOutput/copsub2006.NSF/All%20docs%20by%20catNo/2001~Community%20Profile~POA3187/$File/BCP_POA3187.zip?OpenElement"
#urlfalse = "http://www.censusdata.abs.gov.au/CensusOutput/copsub2006.NSF/All%20docs%20by%20catNo/2001~Community%20Profile~POA0100/$File/BCP_POA0100.zip?OpenElement"

POA_list_2001 = rep(0,10000)

# Post codes 0100-999
for (i in 100:999) {
  POA <- paste0("0",toString(i))
  url_temp <- paste0(url_p1, POA, url_p2, POA, url_p3)
  dest_temp = paste0("/Users/Jeremy/Documents/R/Data/Raw/ABS2001/POA_Zipped/POA", POA, ".zip") #set destination directory
  if (url.exists(url_temp) == TRUE) {
  download.file(url_temp, dest_temp, quiet = TRUE)
  POA_list_2001[i] = i
  }
  print(POA)
}

#http://www.censusdata.abs.gov.au/CensusOutput/copsub2006.NSF/All%20docs%20by%20catNo/2001~Community%20Profile~POA4228/$File/BCP_POA4228.zip?OpenElement

# Post codes 1000-9999
for (i in 1000:9999) {
  POA <- toString(i)
  url_temp <- paste0(url_p1, POA, url_p2, POA, url_p3)
  dest_temp = paste0("/Users/Jeremy/Documents/R/Data/Raw/ABS2001/POA_Zipped/POA", POA, ".zip") #set destination directory
    if (url.exists(url_temp) == TRUE) {
  download.file(url_temp, dest_temp, quiet = TRUE)
  POA_list_2001[i] = i
    }
  if (i %% 100 == 0) {print(i)}
}
```

Formats the list 
```{r POA_list_2001}
POA_2001 <- data.frame(POA = as.numeric(POA_list_2001)) %>%
  filter(POA != 0) %>%
  mutate(POA = ifelse(POA < 1000, paste0("0", POA), as.character(POA)))
```


Unzip abs 2001
```{r unzip_abs2001, eval = FALSE}
zip_p1 <- "/Users/Jeremy/Documents/R/Data/Raw/ABS2001/POA_Zipped/POA"
zip_p2 <- ".zip"

for (i in 1:nrow(POA_2001)) {
  POA <- POA_2001$POA[i]
  zip_temp <- paste0(zip_p1, POA, zip_p2)
  unzip(zip_temp, exdir = "/Users/Jeremy/Documents/R/Data/Raw/ABS2001/POA_Unzipped", overwrite = TRUE) #set destination directory
}
```


#Download Census data for each POA, 2006

Loop over each POA for 2006
```{r all_2006, eval = FALSE}
url_p1 = "http://www.censusdata.abs.gov.au/CensusOutput/copsub2006.NSF/All%20docs%20by%20catNo/2006~Community%20Profile~POA"
url_p2 = "/$File/BCP_POA"
url_p3 = ".zip?OpenElement"

#urltrue = "http://www.censusdata.abs.gov.au/CensusOutput/copsub2006.NSF/All%20docs%20by%20catNo/2006~Community%20Profile~POA3187/$File/BCP_POA3187.zip?OpenElement"
#urlfalse = "http://www.censusdata.abs.gov.au/CensusOutput/copsub2006.NSF/All%20docs%20by%20catNo/2006~Community%20Profile~POA0100/$File/BCP_POA0100.zip?OpenElement"

POA_list_2006 = rep(0,10000)

# Post codes 0100-999
for (i in 100:999) {
  POA <- paste0("0",toString(i))
  url_temp <- paste0(url_p1, POA, url_p2, POA, url_p3)
  dest_temp = paste0("/Users/Jeremy/Documents/R/Data/Raw/ABS2006/POA_Zipped/POA", POA, ".zip") #set destination directory
  if (url.exists(url_temp) == TRUE) {
  download.file(url_temp, dest_temp, quiet = TRUE)
  POA_list_2006[i] = POA
  }
  if (i %% 100 == 0) {print(i)}
}

# Post codes 1000-9999
for (i in 2023:9999) {
  POA <- toString(i)
  url_temp <- paste0(url_p1, POA, url_p2, POA, url_p3)
  dest_temp = paste0("/Users/Jeremy/Documents/R/Data/Raw/ABS2006/POA_Zipped/POA", POA, ".zip") #set destination directory
    if (url.exists(url_temp) == TRUE) {
  download.file(url_temp, dest_temp, quiet = TRUE)
  POA_list_2006[i] = POA
    }
  if (i %% 100 == 0) {print(i)}
}
```

Formats the list 
```{r POA_list_2006}
POA_2006 <- data.frame(POA = POA_list_2006) %>%
  filter(POA != "0")
```

Unzip abs 2006
```{r unzip_abs2006, eval = FALSE}
zip_p1 <- "/Users/Jeremy/Documents/R/Data/Raw/ABS2006/POA_Zipped/POA"
zip_p2 <- ".zip"

for (i in 1:nrow(POA_2006)) {
  POA <- POA_2006$POA[i]
  zip_temp <- paste0(zip_p1, POA, zip_p2)
  unzip(zip_temp, exdir = "/Users/Jeremy/Documents/R/Data/Raw/ABS2006/POA_Unzipped", overwrite = TRUE) #set destination directory
}

# POA names
#list.files("/Users/Jeremy/Documents/R/Data/Raw/ABS2006/POA_Zipped") %>% substr(4,7) %>% data.frame() -> POA_2006
#colnames(POA_2006) <- "POA"

# Trimming file names
temp <- list.files("/Users/Jeremy/Documents/R/Data/Raw/ABS2006/POA_Unzipped") 

for (i in 1:length(temp)) {
  file_name <- paste0("/Users/Jeremy/Documents/R/Data/Raw/ABS2006/POA_Unzipped/", temp[i])
  file.rename(from = file_name,
              to = paste0(substr(file_name, 1, 41), ".xls"))
}

remove(temp)
```


